\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.3in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{graphicx}

\geometry{left=0.3in, right=0.3in, top=0.3in, bottom=0.3in}
\setlist[itemize]{leftmargin=0.5in,itemsep=0.01em,parsep=0.01em}

\titleformat{\section}{\normalsize\bfseries\color{black}}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{0.5ex plus 1ex minus .1ex}{-1.2ex}

\newcommand{\experienceitem}[2]{%
    \noindent\textbf{#1} \hfill #2 \\
    \vspace{-0.9em}
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\newcommand{\sectionline}[1]{%
    \par\noindent\rule[0.5ex]{\linewidth}{0.5pt}\vspace{-0.3em}%
}

\begin{document}
\begin{center}
   \textbf{\Large Rohan Singh}\\
   
    PUNE, MAHARASHTRA, INDIA \\
    \href{https://rohans21.vercel.app/}{Portfolio} \textbar\ 
    +91-7843032325 \textbar\ 
    \href{mailto:rohans212004@gmail.com}{rohans212004@gmail.com} \textbar\ 
    \href{https://github.com/Rohs21}{GitHub} \textbar\ 
    \href{https://www.linkedin.com/in/rohan-singh-8872322b8/}{LinkedIn}
\end{center}

\vspace{-0.6em}
\section*{EDUCATION}
\sectionline{}
\experienceitem{Bachelor of Engineering (Computer Engineering)}{Aug 2022-May 2026} \\
Zeal College of Engineering and Research, Pune \\
Narhe, Pune

\vspace{-0.1em}
\section*{EXPERIENCE}
\sectionline{}
\experienceitem{Web Developer and Design Intern}{December 2024 - Present} \\
@Akash Dayal Groups
\begin{itemize}[leftmargin=0.5in]
    \item Developed and optimized 8+ responsive, user-friendly pages with reusable components, ensuring seamless performance across devices.
    \item Conducted thorough testing and debugging to enhance page functionality, accessibility, and cross-browser compatibility.
    \item Collaborated on UI/UX improvements, refining layouts and design consistency to elevate user engagement and overall experience.
\end{itemize}

\experienceitem{CP and DSA Team Member}{August 2024 - Present} \\
Google Developer Groups
\begin{itemize}[leftmargin=0.5in]
    \item Provided guidance and resolved doubts related to Competitive Programming (CP) and Data Structures \& Algorithms (DSA).
    \item Led a dedicated CP/DSA cohort, fostering growth among aspiring programmers by curating and sharing daily practice problems, encouraging consistent learning and skill enhancement.
    \item Organized Contests and facilitated post-contest discussions, promoting collaborative learning and deeper understanding of problem-solving strategies.
\end{itemize}

\section*{PROJECTS}
\sectionline{}
\experienceitem{Trip-Ally \textbar\ Node.js, Express.js, React.js, MongoDB Atlas, Tailwind CSS}{\href{https://trip-ally.vercel.app}{(Project Link)}} \\
\vspace{-0.6em}
\begin{itemize}[leftmargin=0.5in]
    \item Developed a secure and efficient trip booking platform, Trip-Ally, using React for a seamless user experience, integrating JWT authentication and password hashing for robust data protection.
    \item Optimized backend workflows to streamline booking operations, ensuring fast processing and secure user verification, enhancing overall platform performance.
    \item Implemented a structured authentication system that safeguards user credentials while improving system responsiveness, leading to a more reliable and secure booking process.
\end{itemize}

\experienceitem{BOOKS-HUB \textbar\ React.js, HTML, CSS, JavaScript, API, Git}{\href{https://github.com/Rohs21/Books-app}{(Project Link)}} \\
\vspace{-0.6em}
\begin{itemize}[leftmargin=0.5in]
    \item Built an interactive React-based Book Hub web app featuring book search, trending titles.
    \item Implemented effective state management and utilized Git for version control, streamlining collaboration and boosting development efficiency by 30\%.
    \item Integrated a third-party API to fetch real-time book data, enabling users to explore trending books, detailed information, and create custom favourites.
    \item Delivered a high-performance application with responsive design and seamless real-time updates, enhancing user engagement and satisfaction.
\end{itemize}

\section*{SKILLS}
\sectionline{}
\begin{itemize}[leftmargin=0.5in]
    \item \textbf{Languages:} C/C++, Java, JavaScript, TypeScript, HTML/CSS
    \item \textbf{Frameworks:} React.js, Express, Node.js
    \item \textbf{Libraries:} Tailwind, React Router, Redux, Recoil
    \item \textbf{Developer Tools:} Git, GitHub, Visual Studio, Postman
    \item \textbf{Databases:} SQL(Postgres), MongoDB
    \item \textbf{Relevant Courses:} Data Structure and Algorithm, Database and Management System, Object Oriented programming, Software Engineering
\end{itemize}

\section*{ACHIEVEMENTS AND CO-CURRICULAR}
\sectionline{}
\begin{itemize}[leftmargin=0.5in]
    \item Solved 350+ problems across coding platforms like \href{https://leetcode.com/u/Rohan_s21/}{LeetCode} and \href{https://www.codechef.com/users/rohan_s21}{CodeChef}.
    \item 3rd Rank Winner of Snap-AR Quiz Hackathon - Mumbai.
    \item Institute Rank Top 5 in CodeChef over all the Students.
    \item Secured rank in Top 15\% among 400000+ students in MHT-CET 2022 engineering entrance exam.
    \item Working as a part of Technical Team \& Social-Media manager of ISKCON since 2022.
\end{itemize}

\end{document}